---
title: "Data"
---

**Variables**

<br /> **YEAR:** The data was collected in 2017
<br /> **INCTOT:** INCTOT reports each person’s total annual income or losses from all sources in the previous calendar year
<br /> **NCHILD:** The number of own children residing with each individual. (Including step-children, adopted children, biological children)
<br /> **AGE:** AGE reports the person’s age in years as of the last birthday
<br /> **MARST(Marital Status):** 
<br />1 - Married, spouse presented; 
<br />2 - Married, spouse absent; 
<br />3 - Separated; 
<br />4 - Divorced; 
<br />5 - Widowed; 
<br />6 - Never Married

<br /> 
**Summary Statistic**

<br /> **Income**
```{r}
usa2017 <- usa2017 %>% filter(AGE > 17) 
usa2017 <- usa2017 %>% mutate(divorce = ifelse(MARST == 4, 1, 0))
usa2017 %>% summarise(Max = max(INCTOT), Min = min(INCTOT), Median = median(INCTOT), Mean = mean(INCTOT), SD = sd(INCTOT))
```

<br /> **Age**
```{r}
usa2017 %>% summarise(Max = max(AGE), Min = min(AGE), Median = median(AGE), Mean = mean(AGE), SD = sd(AGE))
```

<br /> **Number of Children**
```{r}
usa2017 %>% summarise(Max = max(NCHILD), Min = min(NCHILD), Median = median(NCHILD), Mean = mean(NCHILD), SD = sd(NCHILD))
```

